\documentclass[11pt,a4paper]{article}

% ── Packages ─────────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{lineno}

% siunitx-lite: format numbers without the full siunitx package
\newcommand{\num}[1]{\ensuremath{\mathrm{#1}}}

\graphicspath{{fig/}}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!60!black,
    citecolor=green!50!black,
    urlcolor=blue!70!black,
}

\onehalfspacing
\linenumbers

% ── Title ─────────────────────────────────────────────────────────────
\title{%
  \textbf{Plant Science is Reorganizing Around Climate-Relevant Crops:\\
  Evidence from 4.9 Million Publications}
}

\author{%
  Ehsan Estaji\textsuperscript{1},
  Jian-Feng Mao\textsuperscript{1,*}
  \\[0.5em]
  \small \textsuperscript{1}Ume\aa\ Plant Science Centre (UPSC), Department of
         Plant Physiology, Ume\aa\ University, Ume\aa, Sweden \\[0.3em]
  \small \textsuperscript{*}Corresponding author: \texttt{jianfeng.mao@umu.se}
  \\[0.2em]
  \small ORCID: E.E.\ 0009-0005-0838-228X;\ \ J.-F.M.\ 0000-0001-9735-8516
}

\date{}

\begin{document}
\maketitle

% ── Abstract ─────────────────────────────────────────────────────────
\begin{abstract}
Whether plant science is pivoting toward climate-resilient crops
remains an open empirical question. Analysing \num{4.9} million
publications (1900--2024) from OpenAlex and PubMed, we find that
annual output over the modern era (1990--2024) follows a logistic
trajectory ($K = 217{,}781$ papers/year, inflection 2006), ending
exponential expansion. \textit{Arabidopsis thaliana}'s share has declined since
2012 while rice, wheat, and maize have risen; 40 sleeping-beauty
papers on minor crops awoke in 2019--2022; CRISPR reached mainstream
adoption twice as fast as prior genomic tools. A persistent
orphan-crop attention gap shows the realignment is incomplete. A
temporal placebo against a 1970--1999 null window (permutation
$p = 0.001$) confirms the shift is era-specific. Citation-flow
analysis reframes the \textit{Arabidopsis} decline as consolidation:
the crop-paper citation share to \textit{Arabidopsis} grew nine-fold
(1995--2016) and the reverse-translation lag collapsed from 6.5 to
2 years.
\textit{Arabidopsis} has become crop science's foundational
methodological substrate.
\end{abstract}

\textbf{Keywords:} plant science, paradigm shift, crop research,
\textit{Arabidopsis}, CRISPR, sleeping beauty, food security, bibliometrics

\clearpage

% ── Main sections ─────────────────────────────────────────────────────
\input{sections/main_text}

% ── Online Methods ────────────────────────────────────────────────────
\section*{Online Methods}
\input{sections/methods}

% ── Extended Data ─────────────────────────────────────────────────────
\clearpage
\section*{Extended Data}
\input{sections/extended_data}

% ── Data Availability ─────────────────────────────────────────────────
\section*{Data Availability}
The OpenAlex and PubMed bibliographic records used in this study are
publicly available from \url{https://openalex.org} and
\url{https://pubmed.ncbi.nlm.nih.gov}, respectively.
The processed corpus (deduplicated DOI list, organism and paradigm
classification labels, BERTopic topic assignments, and derived
result tables) is archived at Zenodo:
\url{https://doi.org/10.5281/zenodo.21199139}.
FAO production statistics used for the research-attention gap analysis
are available from \url{https://www.fao.org/faostat/}.

% ── Code Availability ─────────────────────────────────────────────────
\section*{Code Availability}
All analysis code, SLURM batch scripts, and figure generation scripts
are available at
\url{https://github.com/ehsanestaji/plant-science-paradigm-shift}
under the MIT licence.
The GPU-accelerated embedding and classification pipeline requires
PyTorch~2.7.1 and an NVIDIA A100 GPU; all other analysis scripts are
CPU-only and can be run on a standard workstation with 64\,GB RAM.
A reproducible environment specification (\texttt{requirements.txt} and
\texttt{environment.yml}) is included in the repository root.

% ── Author Contributions ──────────────────────────────────────────────
\section*{Author Contributions}
E.E.\ and J.-F.M.\ conceived the study. E.E.\ designed and performed all
analyses and wrote the manuscript. J.-F.M.\ contributed critical revisions
to the manuscript. All authors read and approved the final version.

% ── Competing Interests ───────────────────────────────────────────────
\section*{Competing Interests}
The authors declare no competing interests.

% ── Funding ───────────────────────────────────────────────────────────
\section*{Funding}
This work was partially supported by the Wallenberg Initiatives in Forest
Research (WIFORCE), funded by the Knut and Alice Wallenberg Foundation.

% ── Acknowledgments ───────────────────────────────────────────────────
\section*{Acknowledgments}
We thank OpenAlex, PubMed, and FAO for openly releasing the
bibliographic and agricultural-production data on which this study
depends. Computational resources for the GPU-accelerated embedding
and classification pipeline were provided by HPC2N (Umeå) via
project \texttt{hpc2n2025-278}; post-hoc robustness and insights
analyses were run on local Apple Silicon workstations. We thank the
\texttt{leidenalg}, \texttt{igraph}, \texttt{DuckDB}, \texttt{BERTopic},
and \texttt{SPECTER2} open-source maintainers whose tools underpin
the analyses reported here.

% ── References ────────────────────────────────────────────────────────
\bibliographystyle{naturemag}
\bibliography{references}

% ── Index of display items and supplementary materials ────────────────
% (placed after the reference list, before the Supplementary Information)
\clearpage
\input{sections/item_lists}

% ── Supplementary Information (placed at the end of the document) ──────
\clearpage
\appendix
\section*{Supplementary Information}
\input{sections/supplementary}

\end{document}
