% ============================================================
%  Paper A — Index of display items and supplementary materials
%  Numbers are pulled via \ref so they stay in sync with the
%  actual figure/table/note counters.
% ============================================================

\section*{List of Main-Text Display Items}

\subsection*{Main-text figures}
\begin{itemize}\setlength{\itemsep}{2pt}
  \item \textbf{Figure~\ref{fig:FA1}.} Logistic growth plateau in plant
        science publications.
  \item \textbf{Figure~\ref{fig:M9}.} \textit{Arabidopsis} consolidates as
        crop science's methodological substrate (instrumentalization ratio
        and reverse-translation lag).
  \item \textbf{Figure~\ref{fig:M1}.} Organism-share time series from
        zero-shot classification (2.77 million papers).
  \item \textbf{Figure~\ref{fig:FA3}.} Sleeping-beauty awakenings cluster in
        2019--2022.
  \item \textbf{Figure~\ref{fig:FA4}.} Method-diffusion S-curves in plant
        science.
  \item \textbf{Figure~\ref{fig:FA6}.} The orphan-organism
        research-attention gap.
\end{itemize}

\subsection*{Main-text tables}
None. The main text contains no tables; all tabular data are provided as
Supplementary Tables (below).

\subsection*{Extended Data figures}
\begin{itemize}\setlength{\itemsep}{2pt}
  \item \textbf{Extended Data Fig.~\ref{fig:FA2}.} Model-organism decline and
        crop-species ascent.
  \item \textbf{Extended Data Fig.~\ref{fig:M2}.} \textit{Arabidopsis} versus
        crop species --- head-to-head share comparison.
  \item \textbf{Extended Data Fig.~\ref{fig:M3}.} Applied versus fundamental
        paradigm by organism.
  \item \textbf{Extended Data Fig.~\ref{fig:M8}.} CRISPR-Cas9 adoption curves
        by organism.
  \item \textbf{Extended Data Fig.~\ref{fig:M4}.} Topic landscape of plant
        science (SPECTER2 + UMAP).
  \item \textbf{Extended Data Fig.~\ref{fig:M5}.} Macro-theme growth/decline
        by decade.
  \item \textbf{Extended Data Fig.~\ref{fig:M6}.} Organism--topic enrichment
        matrix.
  \item \textbf{Extended Data Fig.~\ref{fig:M7}.} Semantic drift of organism
        centroids toward \textit{Arabidopsis}.
  \item \textbf{Extended Data Fig.~\ref{fig:FA5}.} Six intellectual epochs
        defined by concept marriages.
\end{itemize}

\clearpage
\section*{List of Supplementary Materials}

\subsection*{Supplementary figures}
\begin{itemize}\setlength{\itemsep}{2pt}
  \item \textbf{Supplementary Fig.~\ref{fig:S1}.} Annual growth rates by
        organism (classified corpus).
  \item \textbf{Supplementary Fig.~\ref{fig:S2}.} Citation impact by paradigm
        and organism.
  \item \textbf{Supplementary Fig.~\ref{fig:S3}.} Shannon entropy of the
        macro-theme distribution by year.
  \item \textbf{Supplementary Fig.~\ref{fig:S6}.} CD disruption index by
        organism.
  \item \textbf{Supplementary Fig.~\ref{fig:S9}.} Cross-citation matrix
        between organism categories.
  \item \textbf{Supplementary Fig.~\ref{fig:S10}.} International collaboration
        rate by organism.
  \item \textbf{Supplementary Fig.~\ref{fig:s-temporal-placebo}.} Temporal
        placebo test.
  \item \textbf{Supplementary Fig.~\ref{fig:s-growth-aic}.} Growth-model
        comparison (logistic, Gompertz, Richards).
  \item \textbf{Supplementary Fig.~\ref{fig:s-climate-shocks}.} Pooled
        climate-event publication response.
  \item \textbf{Supplementary Fig.~\ref{fig:s-bridge-impact}.} Mean
        citations-per-paper by paradigm class.
  \item \textbf{Supplementary Fig.~\ref{fig:s-paradigm-alignment}.} Paradigm
        alignment in the coauthor graph.
  \item \textbf{Supplementary Fig.~\ref{fig:s-jaccard-over-time}.} Jaccard
        overlap of consecutive-window top-100 reference sets.
  \item \textbf{Supplementary Fig.~\ref{fig:s-reference-half-life}.} Reference
        half-life.
  \item \textbf{Supplementary Fig.~\ref{fig:s-composition-over-time}.}
        Top-100 canon composition, 1995--2024.
  \item \textbf{Supplementary Fig.~\ref{fig:s-top-substitution-pair}.} Top
        anti-correlated (fallen $\times$ riser) citation trajectories.
\end{itemize}

\subsection*{Supplementary tables}
\begin{itemize}\setlength{\itemsep}{2pt}
  \item \textbf{Supplementary Table~\ref{tab:S1}.} Crops ranked by
        research-attention gap.
  \item \textbf{Supplementary Table~\ref{tab:S2}.} Top sleeping-beauty papers
        by $B$-index.
  \item \textbf{Supplementary Table~\ref{tab:S3}.} Logistic diffusion-model
        parameters for methodologies.
  \item \textbf{Supplementary Table~\ref{tab:S7}.} Three-way comparison of
        sigmoidal growth-model fits.
  \item \textbf{Supplementary Table~\ref{tab:S11-risers}.} Top-5 risers in the
        2020--24 top-100 reference list.
  \item \textbf{Supplementary Table~\ref{tab:S11-fallen}.} Top-5 fallen
        classics.
  \item \textbf{Supplementary Table~\ref{tab:S11-substitution}.} Top
        anti-correlated (fallen $\times$ riser) reference pairs.
\end{itemize}

\subsection*{Supplementary notes}
\begin{itemize}\setlength{\itemsep}{2pt}
  \item \textbf{Supplementary Note~\ref{sec:temporal-placebo}.} Temporal
        placebo test (reorganization signal).
  \item \textbf{Supplementary Note~\ref{sec:growth-model-aic}.} Growth-model
        selection --- logistic vs Gompertz vs Richards.
  \item \textbf{Supplementary Note~\ref{sec:climate-shocks}.} Climate-shock
        event study (pooled difference-in-differences).
  \item \textbf{Supplementary Note~\ref{sec:bridge-scientists}.}
        Paradigm-bridging authors --- pre-registered matched-impact analysis.
  \item \textbf{Supplementary Note~\ref{sec:coauthor-alignment}.} Coauthor
        paradigm alignment over time (network-only).
  \item \textbf{Supplementary Note~\ref{sec:canon-churn}.} Canon churn ---
        the plant-science reading list, 1995--2024 (incl.\ canon substitution).
\end{itemize}
